A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-14 introduction.tex
capitalization

In this work, we introduce Ruxanne, a tool for analyzing and extracting fix patterns in Rust. Ruxanne uses a novel embedding of Rust code into fixed-sized vectors. Through Ruxanne, we mined the top 18 most-starred Rust projects in Github to discover the most common bug fix patterns committed to their repositories. We analyzed 87,726 code changes drawn from 57,214 commits across these 18 projects. After clustering the code changes, and conducting a manual analysis, we discovered 20 groups of cross-project bug fix patterns, which we categorize as (1) general patterns and (2) borrow-checker-related patterns. We describe each of these patterns. The most common general pattern is addition or removal of struct fields, while the most common borrow-checker-related bug fix pattern is removing a call to the clone() function. Our patterns can serve as knowledge to be embedded into the design of novel Rust automated program repair tools; we present some specific potential applications of these patterns below.

>>>>

In this work, we introduce Ruxanne, a tool for analyzing and extracting fix patterns in Rust. Ruxanne uses a novel embedding of Rust code into fixed-sized vectors. Through Ruxanne, we mined the top 18 most-starred Rust projects in GitHub to discover the most common bug fix patterns committed to their repositories. We analyzed 87,726 code changes drawn from 57,214 commits across these 18 projects. After clustering the code changes, and conducting a manual analysis, we discovered 20 groups of cross-project bug fix patterns, which we categorize as (1) general patterns and (2) borrow-checker-related patterns. We describe each of these patterns. The most common general pattern is addition or removal of struct fields, while the most common borrow-checker-related bug fix pattern is removing a call to the clone() function. Our patterns can serve as knowledge to be embedded into the design of novel Rust automated program repair tools; we present some specific potential applications of these patterns below.
